---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)
```

# togglvis

<!-- badges: start -->
<!-- badges: end -->


## Installation

You can install the latest version  of togglvis from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("remotes")
remotes::install_github("karissawhiting/togglvis")
```

## Example

This is a basic example showing how to get data from the 
[{togglr}](https://github.com/ThinkR-open/togglr) API and process and visualize it.

You will need to set up an account on [toggl](https://toggl.com/) and get an API token. 
See [{togglr}](https://github.com/ThinkR-open/togglr) for easy instructions on how to set API key. 

Note: You can also download data as a csv directly from the [toggl](https://toggl.com/). 

```{r example}
library(togglvis)
library(dplyr)
library(togglr)
```

```{r, echo=FALSE}
load(here::here("data-raw", "report.RData"))
```

Get summary report data using [{togglr}](https://github.com/ThinkR-open/togglr) app, or download data from toggl web browser. 

```{r, eval = FALSE}
# See togglr documentation for how to set up the API key
report <- togglr::get_detailled_report()

```


```{r cars}
processed_report <- process_report(report)
time_bar_chart(processed_report)

```

